
---
title: 'Lab 11:   Data Cleaning Skills'
author: Yasmine Pascal
date: 04/22/2022
output: word_document
---

## Instructions
This document is the template you will use to type up your responses to the lab exercises that you can find on Canvas.

To complete the lab type your BRIEF answers and the R code in the spaces provided below, according to these guidelines:

  * In general, if an exercise is numbered you will submit the R code that you used to answer the question in the gray area between the three ` marks.  
  * If you need to submit an answer in addition to the code type this between the line that starts #### and the beginning of the gray area for the code.
  * Do not ever type the `View()` command in a lab report.  This works only in RStudio on your computer, so don't include that command in your lab report or you will not be able to compile the document, a process called *knitting*.
  * To produce a document that you can submit on Canvas just click on the Knit button in the upper left quadrant of RStudio.
  * We recommend pressing the Knit button after entering each answer:  it's very common to get errors, and they're easier to fix if you can easily isolate the code that caused the error.
  * The Knit button will create two files:  one is a .Rmd file (R Markdown) and the other is an .docx file.  You will need to submit both these documents for the lab assignment on Canvas.



## Preliminaries
#### Exercise 1

```{r}
library(tidyverse)
library(ggformula)
library(mosaic)
library(dplyr)
library(janitor)
library(stringr)


```

## Read in the  data

#### Exercise 2
18979 players are included in the data set and there are 77 variables
```{r}
library(readr)
FIFA21 <- read_csv("fifa21_raw.csv")
View(FIFA21)
dim(FIFA21)




```

## Cleaning activities

#### Exercise 3
The name of the 19th column before cleaning is "LoanDateEnd" and after cleaning is "loan_date_end". 
```{r}
summary(FIFA21)
FIFA21 <- clean_names(FIFA21)



```


#### Exercise 4
The median weight of players in the FIFA21 data is 165 lbs.
```{r}
tally(~weight, data= FIFA21)
FIFA21<- mutate(FIFA21, weight = str_remove_all(weight, "lbs"))
FIFA21 <- mutate( FIFA21,as.numeric(weight))
favstats(~weight, data= FIFA21)

```


#### Exercise 5
The median height of players in the FIFA21 data set is 6'1"
```{r}
tally(~height, data = FIFA21)
FIFA21 <- mutate(FIFA21, height = str_remove_all(height, "[[**'**]]"))
FIFA21 <- mutate(FIFA21, height = str_remove_all(height, '"'))
FIFA21 <- mutate(FIFA21, height = as.numeric(height))
favstats(~height, data=FIFA21)

```



#### Exercise 6

```{r}
FIFA21<- separate(FIFA21, height, sep = 1, into=c("feet", "inches"))
FIFA21 <- mutate(FIFA21, feet = as.numeric(feet))
FIFA21 <- mutate(FIFA21, inches = as.numeric(inches))
FIFA21 <- mutate(FIFA21, hgt_inches = feet*12 +inches)
favstats(~hgt_inches, data = FIFA21)
```


#### Exercise 7
10005 players are categorized as average in the FIFA21 data set. 
```{r}
FIFA21<- mutate(FIFA21, hgt_group = case_when(hgt_inches >= 73 ~ "tall", TRUE ~case_when(hgt_inches >= 69 ~ "average", TRUE ~ "short")))
tally(~hgt_group, data = FIFA21)



```


#### Exercise 8
```{r}
FIFA21 <- mutate(FIFA21, hgt_group = fct_relevel(hgt_group,c("short", "average", "tall")))
gf_bar(~hgt_group, data = FIFA21)



```

