
---
title: 'Lab 4:  Manipulate data with dplyr'
author: Yasmine Pascal
date: 02/11/2022
output:
  word_document
---

## Instructions
This document is the template you will use to type up your responses to the lab exercises that you can find on Canvas.

To complete the lab type your BRIEF answers and the R code in the spaces provided below, according to these guidelines:

  * In general, if an exercise is numbered you will submit the R code that you used to answer the question in the gray area between the three ` marks.  
  * If you need to submit an answer in addition to the code type this between the line that starts #### and the beginning of the gray area for the code.
  * Do not ever type the `View()` command in a lab report.  This works only in RStudio on your computer, so don't include that command in your lab report or you will not be able to compile the document, a process called *knitting*.
  * To produce a document that you can submit on Canvas just click on the Knit button in the upper left quadrant of RStudio.
  * We recommend pressing the Knit button after entering each answer:  it's very common to get errors, and they're easier to fix if you can easily isolate the code that caused the error.
  * The Knit button will create two files:  one is a .Rmd file (R Markdown) and the other is an .docx file.  You will need to submit both these documents for the lab assignment on Canvas.


## Preliminaries

#### Exercise 1

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(mosaic)
library(ggformula)
library(data1135)

```

## Preliminary data analysis
#### Exercise 2
This data was collected from January 1st 2016 to July 31st 2016. 
```{r}
summary(GoogleAnalyticsData)
dim(GoogleAnalyticsData)

```

## Wringing insights from data

#### Exercise 3

```{r}
GoogleAnalyticsData <- mutate(GoogleAnalyticsData, bounce_rate = bounces / entrances)

```

#### Exercise 4
The proportion of rows in which the bounce rate is greater than 50% is .5898
```{r}
prop( ~ (bounce_rate > .5), data= GoogleAnalyticsData, success = TRUE)

```

## Display Advertising

#### Exercise 5

```{r}
displayAds <- filter(GoogleAnalyticsData, channelGrouping == "Display")

```

#### Exercise 6

Tablets have the greatest number of outliers, which means that they have the most observations which lie a considerable distance away from the data, which could infer that other factors are affecting tablet users. Desktop has the largest IQR which means that 50% of its data is spread out further compared to devices like mobile where 50% of its data is clustered tightly together. 
```{r}
gf_boxplot(bounce_rate ~ deviceCategory, data= displayAds)



```


## Display advertising vs email on mobile devices

#### Exercise 7

```{r}
mobileDevs <- filter(GoogleAnalyticsData, deviceCategory == "mobile",channelGrouping == "Email" |channelGrouping == "Display")


```


#### Exercise 8
On average, display has a greater bounce rate than email, which means that users who receive an email are more likely to explore further than the first page on their website. 
```{r}
favstats( ~bounce_rate | channelGrouping, data= mobileDevs)


```