

---
title: 'Lab 7:  One Sample Hypothesis Tests for the Proportion'
author: Yasmine Pascal 
date: 03/16/2022
output:
  word_document
---

## Instructions
This document is the template you will use to type up your responses to the lab exercises that you can find on Canvas.

To complete the lab type your BRIEF answers and the R code in the spaces provided below, according to these guidelines:

  * In general, if an exercise is numbered you will submit the R code that you used to answer the question in the gray area between the three ` marks.  
  * If you need to submit an answer in addition to the code type this between the line that starts #### and the beginning of the gray area for the code.
  * Do not ever type the `View()` command in a lab report.  This works only in RStudio on your computer, so don't include that command in your lab report or you will not be able to compile the document, a process called *knitting*.
  * To produce a document that you can submit on Canvas just click on the Knit button in the upper left quadrant of RStudio.
  * We recommend pressing the Knit button after entering each answer:  it's very common to get errors, and they're easier to fix if you can easily isolate the code that caused the error.
  * The Knit button will create two files:  one is a .Rmd file (R Markdown) and the other is an .docx file.  You will need to submit both these documents for the lab assignment on Canvas.



## Preliminaries

#### Exercise 1

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggformula)
library(mosaic)
library(data1135)
```

## Preliminary Data Analysis

#### Exercise 2
1.39% of policy holders made a claim. 
```{r}
summary(mortality)
dim(mortality)
prop(~(Claimed == 1), data= mortality, success= "TRUE")
```

#### Exercise 3
The Central Limit Theorem holds because the observations are independent and both np0 and n(1−p0) are greater than 10. 
```{r}
nrow(mortality) * .011
nrow(mortality) * (1-.011)
```

#### Exercise 4:
The test statistic is 1.23 and the p-value of the test statistic is 0.1093
```{r}
prop.test(~Claimed, data = mortality, success = "1", correct= FALSE, p= 0.011, alternative= "greater")

```


#### Exercise 5:

We fail to reject the original hypothesis (HO). We do this because our p- value (0.1093) is greater than a (0.05). 



#### Exercise 6:
There is not statistically significant evidence that the proportion of claims has increased from 1.1%


## Using confidence intervals to carry out two-tailed hypothesis tests

#### Exercise 7:

```{r}
binom.test(~Claimed, data= mortality, success= "1", ci.method = "Wald", conf.level= .95)

```


#### Exercise 8:

We fail to reject the original hypothesis because the hypothesized value of the population parameter (0.014) falls within the confidence interval [0.009,0.019]. There is not practically significant evidence that the mortality rate has changed. 

